% !TeX root = disseration.tex
\chapter{Author's Publications on this topic}
\noindent The work in this document is partially based on the following related publications.
\begin{enumerate}
	\item \textbf{He, Y.} (2019): Recommending Privacy Settings for IoT. In 24th International Conference on Intelligent User Interfaces (IUI ’19 Companion), March 17--20, 2019, Marina del Ray, CA.
	
	\item \textbf{He, Y.}, Bahirat, P., Knijnenburg, B.P. (2018): A Data Driven approach to Designing for Privacy in Household IoT. ACM Transactions on Interactive Intelligent Systems (TiiS).
	
	\item Sanchez, O., Torre, I.,\textbf{ He, Y.}, Knijnenburg, B.P. (2018) A Recommendation Approach for User Privacy Preferences in the Fitness Domain. User Modeling and User-Adapted Interaction (UMUAI).
	
	\item Bahirat, P., \textbf{He, Y.}, Knijnenburg, B.P. (2018): Exploring Defaults and Framing effects on Privacy Decision Making in Smarthomes. Interactive Workshop on the Human aspect of Smarthome Security and Privacy, SOUPS 2018, Baltimore, U.S.A.
	\item Bahirat, P., \textbf{He, Y.}, Menon, A., Knijnenburg, B.P. (2018): A Data-Driven Approach to Developing IoT Privacy-Setting Interfaces. In 23th International Conference on Intelligent User Interfaces, 2018, Tokyo, Japan.
	
	
%	
%Following are other publications that I have during my Ph.D.
%	\item Liu, J., Shen, H., Yu, L., Narman, H.S., Zhai, J., Hallstrom, J.O., He, Y. (2018): Characterizing Data Deliverability of Greedy Routing in Wireless Sensor Networks. IEEE Transactions on Mobile Computing (TMC) 17, 543-559.
%	\item Ge, R., Feng, X., He, Y., Zou, P. (2017): The Case for Cross-Component Power Coordination on Power Bounded Systems. ICPP2016, Philadelphia, PA, USA
%	\item Zhai, J., He, Y., Hallstrom, J.O. (2015): A Software Approach to Protecting Embedded System Memory from Single Event Upsets. EWSN2015, Porto, Portugal.
%	\item He, Y., Du, Y., Hughes, S., Zhai, J., Hallstrom, J.O., Sridhar, N. (2015): DESAL$^\beta$ : A Framework For Implementing Self-stabilizing Embedded Network Applications. International Internet of Things Summit, pp. 307-312. Springer, Cham, 2015.
%	\item Ruffing M., He Y., Kelly, M., Hallstrom, J.O., Olariu, S., Weigle, M.C. (2014): A Retasking Framework for Wireless Sensor Networks. Military Communications Conference (MILCOM), 2014 IEEE 1066-1071.
\end{enumerate}